---
title: "simpleRegress"
author: "put your name here"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```


## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

The plot that relates the variables LENGTH and NECK has a higher adjusted r-squared value (.7423) as compared to the relationship between LENGTH and WEIGHT variables. Additionally, the former yields a smaller residual strand error value(5.367), while the latter carried 5.432 degrees of freedom. When considering this data, the variable NECK seems to be more accurate predictor of LENGTH and WEIGHT. 

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

The relative residual error and adjusted r-square values are too high and low, respectively, as compared to the aforementioned variables, indicating the relationship between AGE and LENGTH is weak.   

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

The scatter-plot detailing the relationship between LENGTH and HEADWTH, when computed, a higher residual standard error and lesser adjusted r-squared compared to the scatter-plot between LENGTH and NECK. 














